Towards the near-infrared detection of brown dwarf companions: Exploring methods to detect low mass stellar companions from blended spectra \thanks{Based on observations collected at the European Organisation for Astronomical Research in the Southern Hemisphere under ESO programme 089.C-0977(A)}

### 2018-08-06 nir_companions.tex
Add CRIRES-POP mismatch check.

>>>>

{\rd To specifically check that the mismatch was not due to errors in our reduction we obtained the final spectral atlas of {10 LEO} from the CRIRES-POP archive, fully reduced and telluric corrected  \citep{nicholls_crirespop_2017}. Comparing the spectrum of {10 LEO} to a PHOENIX-ACES model with the corresponding parameters \(T_{\textrm{eff}_1}=4800\)~K, logg=3.0, [Fe/H] = 0.0 and convolved to R=90\,000,  similar line mismatches are observed. For 10 LEO, there is more spectral lines that agree with the model, but in the region of our observations between 2110--2160~nm there are deep lines in the model that are not observed, lines that have significantly different strengths, lines observed that are not modelled whilst other lines `appear' to be offset in wavelength, at the same positions observed in the work presented here. This indicates that the mismatch is not specific to our reduction only and that there is still room for improvement in synthetic models around 2100~nm.}
